---
title: "p8105_hw5_cy2588"
author: "Chufeng Yang"
date: "2020/11/14"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

### Solution 1
Read in the data.

```{r}
homicide_df = 
  read_csv("p1_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```
Summarize
```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

prop test for a single city

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Iterate

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

Create a plot
```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

### Solution 2

Clean the data
```{r, error = TRUE}
homicide_df_2 = 
  read_csv("p1_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```
Build a function of prop test
```{r, error = TRUE}
city_prop_test = function(df) {
  
  n_unsovled = as.numeric(summarize(df,sum(resolved == "unsolved")))
  n_total = as.numeric(summarize(df,n()))
  
  prop.test(n_unsovled, n_total)
  
}
```

map function with data



```{r, error = TRUE}
results_df_2 = 
  homicide_df_2 %>% 
  mutate(
    prop_tests_2 = map(homicide_df_2$data, city_prop_test),
    tidy_tests_2 = map(.x = prop_tests_2, ~broom::tidy(.x))
) %>%
  select(-prop_tests_2) %>% 
  unnest(tidy_tests_2) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

Create a plot
```{r, error = TRUE}
results_df_2 %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

Start with a dataframe containing data from all participants
```{r, error = TRUE}
path_df = 
  tibble(
    path = list.files("p2_data"),
  )
```

Iterate over file names and read in data
```{r}
lda_data = 
  path_df %>%
  mutate(
    path = str_c("p2_data/", path),
    data = map(path, read.csv)) %>%
  unnest(data)
lda_data
```

Tidy the result
```{r}
lda_data_tidy = 
  lda_data %>%
  mutate(
    path = str_remove_all(path,".csv")
  )%>%
  separate(path, into = c("arm","id"), sep = 11)%>%
  mutate(
    arm = str_remove_all(arm, "p2_data/"),
    id = str_remove_all(id, "_"),
    arm = str_replace(arm,"con","control"),
    arm = str_replace(arm,"exp","experiment")
  )%>%
  pivot_longer(
    week_1:week_8,
    names_prefix = "week_",
    names_to = "week",
    values_to = "observations"
  )%>%
  mutate(week = as.numeric(week))
lda_data_tidy
```

Make a spaghetti plot
```{r}
lda_data_tidy %>%
  unite("arm_id",c(arm,id), sep = "_", remove = F)%>%
  ggplot(aes(x = week,
             y = observations))+
  geom_point(aes(color = arm,
                group = id),
             alpha = .5,
             size = .5)+
  geom_path(aes(colour = arm, 
                group = arm_id),
            alpha = .5)+
  geom_smooth(aes(colour = arm), se = F)
```

From the plot above, we could find that the observations of experimental group keep increasing since week 1, and observations of control group are basically  stable. Then we noted that the observations of both groups are close, and observations of experimental group become higher than control group over time.

## Problem3

Set mu = 0
```{r}
set.seed(1)
sim_t = function(n = 30, mu, sigma = 5){

  sim_data_0 = tibble( 
  x = rnorm(n, mean = mu, sd = sigma)
  )
sim_data_0 %>% 
    summarize(
      mu_hat = mean(x),
      p_value = t.test(x, conf.level = 0.95) %>% broom::tidy()%>% pull(p.value),
      mu = mu
    )
  
}

output = vector("list", 5000)

for (i in 1:5000) {
  output[[i]] = sim_t(mu = 0)
}

sim_results = bind_rows(output)
```

Repeat for mu = 1,2,3,4,5,6
```{r}
set.seed(1)
sim = function(n = 30, mu, sigma = 5){
  
  output_all = vector("list", 5000)
  for (i in 1:5000) {
  output_all[[i]] = sim_t(mu = mu)
  }
  sim_results_all = bind_rows(output_all)
}

output_set = vector("list", 6)

for (i in 1:6) {
  output_set[[i]] = sim(mu = i)
}

sim_total = bind_rows(output_set)
```

make plot of the power
```{r message=F, warning=F}
sim_total %>% 
  mutate(mu = as.factor(mu)) %>% 
  filter(p_value <= 0.05) %>% 
  count(mu)%>%
ggplot(aes(x = mu, y = n/5000, fill = mu)) +
  geom_bar(stat="identity", width = ) +
  labs(
    x = "true value of μ",
    y = "power of the test",
    title = "power plot by different μ"
    )
```

According to the plot, we could find the power of the test increased when our true value of μ increasing. When true value of μ equal or greater than 5, power of the test reached maximum.

plot of average estimate and rejected
```{r message=F, warning=F}
mean_data = sim_total %>% 
  group_by(mu) %>% 
  summarize( mean_mu = mean(mu_hat))%>% 
  mutate(group = "all") 
rej_mean_data = sim_total %>% 
  filter(p_value <= 0.05) %>% 
  group_by(mu) %>% 
  summarize( mean_mu = mean(mu_hat))%>% 
  mutate(group = "rej")
p3_plot_data = bind_rows(mean_data, rej_mean_data)

 ggplot(p3_plot_data, aes(x = mu, y = mean_mu, group = group, color = group)) +
  geom_point(aes(color = group), alpha = .5, size = 3) +
  geom_smooth(alpha = .5, size = 0.5) +
  labs(
    x = "true value of μ",
    y = "average estimate",
    title = "average estimate by different μ"
    )
```
























